---
title: "Basis Device Preprocessing and EDA"
author: "Peter Cho"
date: "9/13/2019"
output: pdf_document
---

# Load the libraries
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(Hmisc)
library(mltools)
library(lsr)
library(binr)
library(reshape)
library(RSQLite)
library(ProjectTemplate)
```

# Recreate supplementary figures from open access tidied data set
```{r setup, include=FALSE}
og_clean_PLOS <- readxl::read_xlsx("C:/Users/chope/Downloads/stanford/wearables/Support_data_for_Figures/S4 Fig/FigS4AB.xlsx", col_names = FALSE)
og_clean_PLOS <- t(og_clean_PLOS[,-c(1)]) 
rownames(og_clean_PLOS) <- 1:nrow(og_clean_PLOS)
melt_clean_PLOS = melt(og_clean_PLOS)

ggplot(melt_clean_PLOS, aes(x = X1, y = value, color = as.factor(X2))) +
  geom_line() +
  xlab("Activity Ventile") +
  ylab("HR") + 
  ggtitle("Tidied Data PLOS HR vs. Activity Ventile")
# ggsave("og_PLOS_Figure_Linear.png")

cor_melt_clean_PLOS <- melt_clean_PLOS %>% 
  group_by(X2) %>% 
  summarise(d = cor(1:19, value))

ggplot(cor_melt_clean_PLOS) +
  geom_point(aes(x = X2, y = d))+
  xlab("Participant Number") + 
  ylab("Correlation Coefficient HR~Activity Ventile") + 
  ggtitle("Tidied Data PLOS Correlation Coefficient HR vs. Activity Ventile")
# ggsave("og_PLOS_Figure_Points.png")

```

# Generate supplementary figures from unprocessed watch data set

## Select watch data for one participant. Change path according to file location
```{r setup, include=FALSE}
single_participant <- read.csv("C:/Users/chope/Downloads/stanford/wearables/Transfer Folder/Basis_003.csv") 
```

### Exploratory Analysis and Segmenting
```{r setup, include=FALSE}
colnames(single_participant)
head(single_participant)
portion <- trunc((nrow(single_participant))*0.001)
sample_single_participant <- sample(levels(single_participant$time), portion)
sample_single_participant <- sample(single_participant$hr, portion)
sum(is.na(single_participant$hr))/nrow(single_participant) # simple summary statistics
sum(is.na(single_participant$accel_magnitude))/nrow(single_participant) # simple summary statistics
sum(is.na(single_participant$skin_temp))/nrow(single_participant) # simple summary statistics
```

### Preprocessing Stage
```{r setup, include=FALSE}
cc_single_participant <- single_participant %>%
  select("hr", "accel_magnitude") %>% 
  na.omit() %>% 
  arrange(accel_magnitude) %>% 
  mutate(count = row_number())
rp_data <- tapply(cc_single_participant$hr, cut(cc_single_participant$count, 19), mean)
rp_data
```

### Test code for the ventile calculation
```{r setup, include=FALSE}
complete_clean_single_participant[, "reorder"] <- bin_data(complete_clean_single_participant$accel_magnitude, bins=20, binType = "quantile")
complete_clean_single_participant$reorder <- as.numeric(cut2(complete_clean_single_participant$accel_magnitude, m = length(complete_clean_single_participant$accel_magnitude)/25, g = 40))
complete_clean_single_participant$reorder <- quantileCut(complete_clean_single_participant$accel_magnitude, 20)
complete_clean_single_participant$reorder <- bins.quantiles(complete_clean_single_participant$accel_magnitude, max.breaks = length(complete_clean_single_participant$accel_magnitude)/10, 20)


sim_single_participant <- complete_clean_single_participant %>% 
  group_by(reorder) %>% 
  summarise(avg_hr = mean(hr), number_val = n())
```

## Select watch data for all participants and generate activity ventiles for each participant. Change path according to file location
```{r}
files <- list.files(path="C:/Users/chope/Downloads/stanford/wearables/Transfer Folder", pattern="*.csv", full.names=TRUE, recursive=FALSE)

activity_ventile <- function(single_participant_csv){
  single_participant <- read.csv(single_participant_csv)
  cc_single_participant <- single_participant %>%
    select("hr", "accel_magnitude") %>% 
    na.omit() %>% 
    arrange(accel_magnitude) %>% 
    mutate(count = row_number())
  rp_data <- tapply(cc_single_participant$hr, cut(cc_single_participant$count, 19), mean)
  return(as.data.frame(rp_data))
}

lapply(files, activity_ventile) %>% 
  bind_rows() -> combined_df

raw_PLOS <- data.matrix(combined_df)
raw_PLOS <- matrix(raw_PLOS, nrow = 43, ncol = 19, byrow=TRUE)
raw_PLOS <- as.data.frame(t(raw_PLOS))
```

## Generate the graphs for the raw data
```{r}
raw_PLOS <- raw_PLOS %>% 
  mutate(id = 1:nrow(raw_PLOS))
melt_raw_PLOS <- melt(raw_PLOS, id = "id") 

ggplot(melt_raw_PLOS, aes(x = id, y = value, color = as.factor(variable))) +
  geom_line() +
  xlab("Activity Ventile") +
  ylab("HR") + 
  ggtitle("Raw PLOS HR vs. Activity Ventile")
# ggsave("raw_PLOS_Figure_Linear.png")

cor_melt_raw_PLOS <- melt_raw_PLOS %>% 
  group_by(variable) %>% 
  summarise(d = cor(1:19, value))

ggplot(cor_melt_raw_PLOS) +
  geom_point(aes(x = 1:nrow(cor_melt_raw_PLOS), y = d))+
  xlab("Participant Number") + 
  ylab("Correlation Coefficient HR~Activity Ventile") + 
  ggtitle("Raw PLOS Correlation Coefficient HR vs. Activity Ventile")
# ggsave("raw_PLOS_Figure_Points.png")
```

## Pre-processed PLOS data. Change file path with the preprocessed watch database. Still need to add EDA to this section.
```{r}
filename <- "C:/Users/chope/Google Drive/Grad School/Digital Functional Capacity/wearables_clinical_deID.db"
sqlite.driver <- dbDriver("SQLite")
db <- dbConnect(sqlite.driver,
                dbname = filename)
                
## Some operations
dbListTables(db)
demo_tb <- dbReadTable(db,"demographics")
result_tb <- dbReadTable(db,"lab_results")
link_tb <- dbReadTable(db,"subject_wearable_links")
vitals_tb <- dbReadTable(db,"vitals")
data_tb <- dbReadTable(db,"wearable_data")
dbDisconnect(sqlite.driver, dbname = filename)
```


